Identifying the L1 of non-native writers: the CMU-Haifa system\\[1em] {\large Chris Dyer$^\ast$ Manaal Faruqui$^\ast$ Noam Ordan$^\dagger$ Nathan Schneider$^\ast$\\ Yulia Tsvetkov$^\ast$ Naama Twitto$^\dagger$ Shuly Wintner$^\dagger$}\\[-3em]

### 2013-04-09 paper/paper.tex
abstract

\begin{document}
\maketitle
\begin{abstract}
Given a dataset of English essays composed by non-native speakers, as
part of the TOEFL exam, we identify with high accuracy the native
language of the authors. We use standard text classification
techniques, but define sophisticated classifiers that are sensitive to
the specific patterns observed in the English of authors whose first
language is structurally different. We describe the various features
used for classification, as well as the settings of the classifier
that yielded the highest accuracy.
\end{abstract}

>>>>

\begin{document}
\maketitle
\begin{abstract}
We show that it is possible to learn to identify, with high accuracy, the native language of English test takers writers from the content of the essays they write.  Our method uses standard text classification
techniques based on multiclass logistic regression to exploit in conjunction individually weak indicators to predict the most probable native language from a set of 11 possibilities. We describe the various features
used for classification, as well as the settings of the classifier
that yielded the highest accuracy.
\end{abstract}
